### 2014-11-07 fundamentals/intro.tex

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights into simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE}
while environmental performance might be measured in spent fuel volume, 
  toxicity, or mined uranium.

@@

The \Cyclus simulator emerged from a line of tools seeking to break this practice.  
Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
\gls{GENIUSv1}, the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \gls{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

@@

\Cyclus separates the problem of modeling a
physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
interact with the kernel. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. The archetypes represent 
individual types of facilities and capture their unique physics.  Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), without having to model the entirety of the cycle.

@@

\Cyclus models facilities, institutions, regions, and resources as discrete 
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small 
material objects at isotopic resolution. In this way, the \Cyclus simulator is 
applicable across the full range of modeling extremes.

Although some questions require resolution at the level of 
individual facilities and materials, 
Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials.  As a result, detailed performance 
metrics cannot be captured with previously existing tools.
The generality of \Cyclus therefore enables many use cases 
that cannot be achieved with fleet-based models.

One such example is the use case that seeks to capture system vulnerability to nefarious 
material diversion. Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies, and so this type of analysis requires
 discrete simulation of a 
target facility and the individual materials modified within it. 
Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies. 
Material risk analysis, therefore, demands discretely modeled objects like those 
in the \Cyclus simulator.

There are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
academic researchers, private-industry economic forecasters, and even students 
in engineering courses may benefit from the ease of development and
customization provided by the discrete, modular, agent-based architecture of \Cyclus.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights from simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE}, requiring calculation of
lifetime fuel costs and electricity generation, 
while environmental performance might be measured in spent fuel volume, 
  toxicity, or mined uranium.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

@@

\Cyclus separates the problem of modeling a
physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
interact with the kernel. The kernel is responsible for the
deployment and interaction logic of entities in the simulation.  Physics calculations and 
customized behaviors are implemented within archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), without having to model the entirety of the cycle.

@@

\Cyclus models facilities, institutions, regions, and resources as discrete 
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small 
material objects at isotopic resolution. In this way, \Cyclus is 
applicable across the full range of modeling extremes.

Although some questions require resolution at the level of 
individual facilities and materials, 
Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials.  As a result, many detailed performance 
metrics cannot be captured with previously existing tools.
The generality of \Cyclus therefore enables many use cases 
that cannot be achieved with fleet-based models.

One such use case seeks to capture system vulnerability to nefarious 
material diversion. Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies, and so this type of analysis requires
 discrete simulation of a 
target facility and the individual materials modified within it. 
Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies. 
Material risk analysis, therefore, demands discretely modeled objects like those 
in \Cyclus.

There are a number of types of users and developers who will 
interact with \Cyclus. National laboratory researchers,
academic researchers, private-industry economic forecasters, and even students 
in engineering courses may benefit from the ease of development and
customization provided by the discrete, modular, agent-based architecture of \Cyclus.
